Gaia's constraints on the extremely massive ($\sim$$150\,M_\odot$) runaway star candidate VFTS682

### 2018-06-10 VFTS682_APJL.tex
merging

VFTS682 is identified with the source id 4657685637907503744 in the \emph{Gaia} DR2 catalog  as a 15.65 mag star in the G band \citep{Gaia-Collaboration+2016a, Gaia-Collaboration+2018}.   The number of visibility periods, i.e. groups of observations separated from other groups by a gap of at least 4 days, used in the astrometric solution is 17 for this star. The reported astrometric excess noise is zero. \citep[][]{lindengren:18}.  These values suggest that the \emph{Gaia} DR2  data for VFTS682 are reliable. Generally the Gaia errors are correlated, but the correlation coefficient is small for this star, see Tab.~\ref{tab:vfts682}. We can therefore treat the proper motion components as uncorrelated.

>>>>

VFTS682 is identified with the source id 4657685637907503744 in the \emph{Gaia} DR2 catalog  as a 15.65 mag star in the G band \citep{gaia:16,brown:18}.   The number of visibility periods, i.e. groups of observations separated from other groups by a gap of at least 4 days, used in the astrometric solution is 17 for this star. The reported astrometric excess noise is zero. \citep[][]{lindengren:18}.  These values suggest that the \emph{Gaia} DR2  data for VFTS682 are reliable. Generally the Gaia errors are correlated, but the correlation coefficient is small for this star, see Tab.~\ref{tab:vfts682}. We can therefore treat the proper motion components as uncorrelated.
